Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-01-25 parts/def-ph.tex
sa++

>>>>

Finally, a context (\pref{def:context}) extends the notion of state to a set of possible initial states:
\modMF{
to each automaton in the model, a context maps a set of local states in this automaton.
}
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}
\noindent
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
\begin{comment}
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.

\end{comment}

We also extend the override operator to contexts (\pref{def:ctxcap}).
\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
\label{def:ctxcap}
  For any $\ctx\in\Ctx$ and set of local states $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} \DEF
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}

### 2015-01-25 parts/intro.tex
sa++

\paragraph*{Functions and least fixed point}
If $A$ and $B$ are sets,
$f : A \rightarrow B$ denotes a function $f$ that maps the elements of $A$ to elements of $B$.
If $f$ is a monotonically increasing and bounded function, then
$\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater than $x_0$.

>>>>

\paragraph*{Digraph}
If $(V,E)$ is a directed graph, $V$ are the nodes, $E \subset V\times V$ the edges,
the children of a node $n$ are given by
$\childs: V \to \powerset(V)$, with
$\childs(n) \DEF \{ m\in V\mid (n,m)\in E\}$;
its parents are given by
$\parents: V \to \powerset(V)$ with
$\parents(n) \DEF \{ m\in N\mid (m,n)\in E\}$;
and its descendants are give by
$\conn_{(V,E)}(n)$ which is the least fixed point containing $n$
of the function
$\f{f}\conn:\powerset(N)\to \powerset(N)$
with $\f{f}\conn(W) \DEF \bigcup_{m\in W} \childs(m)$.

%\paragraph*{Functions and least fixed point}
%If $A$ and $B$ are sets,
%$f : A \rightarrow B$ denotes a function $f$ that maps the elements of $A$ to elements of $B$.
%If $f$ is a monotonically increasing and bounded function, then
%$\lfp{x_0}{x}{x'}$ is the least fixed point of the function $x \mapsto x'$ which is greater than $x_0$.

### 2015-01-25 parts/sa.tex
sa++

The aim of searching for the existence of a scenario from a state $s$ leading to a state
where a given local state of an automaton $a_j$ is present
can be reformulated as the checking for the non-emptiness of $\concr(\obj{a_i}{a_j})$, where
$a_i=\get{s}{a}$.
A first hint for checking this emptiness is to look for actions that have to be played in order to
reach the state $i$ from $0$ within the automaton $a$.

@@

\todo{revise}
In the following, we denote: $\sSol = \powerset(\PHproc)$
\moda{%
and $\Sol = \powerset(\sSol)$.
}%
\modMF{%
The elements of $\sSol$ are sets of local states,
and will later represent sets of hitters of a given action
that are required to be active simultaneously in order to play this related action.
The elements in $\Sol$ are sets of sets of hitters,
and represent the requirements to play a whole bounce sequence.
}%

@@

  \noindent
  \modMF{
  As a consequence,
  $\aBS(\obj{a_i}{a_j}) = \emptyset$ if $\BS(\obj{a_i}{a_j}) = \emptyset$,
  and $\BS(\obj{a_i}{a_i}) = \{ \emptyset \}$.
  }%
\end{definition}

@@

These refinements can be summarized compactly with a so-called Local Causality Graph (LCG).
A LCG $\myB = (\cwV, \cwE)$
is a digraph where $\cwV \subseteq \Proc \cup \Obj \cup \sSol \cup \Sol$ is the set of vertices
and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges.
\todo{explain nodes}
Such a graph aims a describing the requirements of a given reachability
problem, that is, the reachability of $\w$ from the initial context $\ctx$.
Thus, a node in $\PHproc$ represents a local state required to play an action,
a node in $\Obj$ is an objective to reach a given local state,
a node in $\sSol$ is a set of hitters that have to be active simultaneously
to solve one step of a given objective,
and a node in $\Sol$ is a set of sets of hitters,
thus encompassing all requirement for the solving of a whole objective.

\todo{explain edges}
The edges of such a graph allow to draw links between these requirements.
Thus, an objective $P \in \Obj$ is solvable if
at least one related bounce sequence in $\BS(P)$ can be played;
therefore, we can consider all minimal sets of sets of hitters of these bounce sequences
(that is, the sets of $\aBS(P) \subseteq \Sol$, see \pref{def:aBS})
as requirements to solve this objective (\pref{eq:ESol1}).
Such a set can then naturally be split into as many sets of hitters (\pref{eq:ESol3})
which all have to be simultaneously active.
These sets of hitters can in turn be split into several local state nodes (\pref{eq:ESol2}).
This creates new requirements, as the reachability of a required local state $a_i$
is approximated by the ability to solve all objectives of the form
$\PHobjp{a}{j}{i} \in \Obj$ for all $a_j$ in the initial context (\pref{eq:EReq}).
Furthermore, we note that the solving of an objective $P$ may require
a local state of $\PHsort(P)$,
\ie $\gCont(\PHsort(P), P) \neq \emptyset$ (see \pref{def:maxCont});
in this case, $P$ is re-targeted (\pref{eq:ECont}).
Finally, \pref{eq:Vw} and \eqref{eq:Vproc}
force the graph to contain all the initial objectives
and the related local states,
and \pref{eq:VE} ensures the consistency of $\cwV$.

\todo{motivate context}
A context (\pref{def:context}) extends the notion of state to a set of possible initial states:
\modMF{
to each automaton in the model, a context maps a set of local states in this automaton.
}
\begin{definition}[Context ($\Ctx$)]
\label{def:context}
  A \emph{context} $\ctx$ associates to each automaton in $\PHs$ a non-empty subset of its local states:
  $\forall a \in \PHs, \PHget{\ctx}{a} \subseteq \PHl_a \wedge \PHget{\ctx}{a} \neq \emptyset$.
  $\Ctx$ is the set of all contexts.
\end{definition}

Given a context $\ctx$ and an objective sequence $\w$, the corresponding LCG can be built
recursively starting from the objectives in $\w$ and recursively adding their possible refinements
following $\BS$ (\pref{def:glc}).

\begin{definition}
\label{def:glc}
Given a context $\ctx$ and a local state $p\in \Proc$,
the Local Causality Graph (LCG) for reachability under-approximation
$\cwB \DEF (\Bv, \Be)$
with
$\cwBNodes \subseteq \Proc \cup \Obj \cup \NSol \cup \powerset(\Proc)$
and
$\cwBEdges \subseteq \cwBNodes \times \cwBNodes$,
is the smallest graph such that:
\begin{enumerate}
\item
$p \in \cwBNodes$
\item
$a_i\in\cwBNodes\cap\Proc \Leftrightarrow \{ (a_i,\obj{a_j}{a_i}) \mid
a_j\in\ctx$ \\
\hspace*{3cm}
$\vee (a_j\neq a_i\wedge a_j\neq\w\wedge a_j\in\cwBNodes\cap\Proc)
\}\subseteq\cwBEdges$
\item
$P\in\cwBNodes\cap\Obj \Leftrightarrow 
	\{ (P,\langle P,nls\rangle) \mid nls\in\nsol(P) \}\subseteq\cwBEdges$
\item
$\langle P, nls \rangle\in\cwBNodes\cap\NSol \Leftrightarrow
	\{ (\langle P,nls\rangle, ls) \mid ls\in nls \}\subseteq\cwBEdges$
\item
$ls \in\cwBNodes\cap\powerset(\Proc) \Leftrightarrow
	\{ (ls, a_i) \mid a_i\in ls \}\subseteq\cwBEdges$
\item
$\obj{a_i}{a_j}\in \cwBNodes\cap\Obj \Rightarrow 
	\{(\obj{a_i}{a_j},\obj{a_k}{a_j}) \mid a_k\neq a_j,$
\\
\hspace*{4cm}
$a_k\in \conn_{(\cwBNodes,\cwBEdges)}(\langle\obj{a_i}{a_j},nls\rangle),$
\\
\hspace*{4cm}
$nls\in\nsol(\obj{a_i}{a_j}) \}\subset\cwBEdges$
\end{enumerate}

\todo{def conn, nsol}
\end{definition}

%
\begin{comment}
\noindent
For a given context $\ctx$, we note $a_i \in \ctx$ if and only if $a_i \in \PHget{\ctx}{a}$,
and for all $ps \in \powerset(\PHproc)$ or $ps \in \PHl$, $ps \subseteq \ctx \EQDEF \forall a_i \in ps, a_i \in \ctx$.
A sequence of actions $\delta$ is \emph{playable} in a context $\ctx$ if and only if 
$\exists s \subseteq \ctx, \delta \in \Sce(s)$.
We denote then: $\delta \in \Sce(\ctx)$,
and the play of $\delta$ in $\ctx$ is $\ctx \PHplay \delta = \ctx \Cap \ceil(\delta)$,
where $\ceil(\delta)$ is the set containing the last local state in the sequence $\delta$ (hitter or bounce) of every automaton mentioned in $\delta$.

\end{comment}

@@

\todo{explain rational}
\begin{itemize}
\item we want to identify an objective sequence that for sure has a concrete scenario
\item LCG is abstract representation of a set of objective sequences
\item we prove that if LCG has no cycle, and all its local states synchronizations are independent,
then such a sequence exists.
\item Note: as we are under-approximating, we de not require that this set is complete.
\end{itemize}

\todo{motivate $\uconcr$}
\begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
\label{def:uconcr}
  \[
  \modMF{\forall \w \in \OS,}
  \uconcr(\w) \DEF
  \begin{cases}
    \concr(\w) & \text{if } \forall s \in \PHl, \concr(\w)\neq\emptyset\\
    \emptyset & \text{else.}
  \end{cases}
  \]
\end{definition}

\todo{revise}
\modMF{
In the saturated graph of local causality, a set of hitters $A \in \sSol$
is said to be \emph{coherent} (\pref{def:coherent})
if none of the local states in $A$ conflict with
a successor of $A$ in $\Bv \cap \Proc$,
that is, if there exists no local state node $a_j$ in the successors of $A$
and no element $a_i \in A$ so that $a_i \neq a_j$.
}
\begin{definition}[Independant synchronisations]
\label{def:coherent}
  In a LCG $\cwB = (\Bv, \Be)$,
  a node $x \in \Bv\cap\sSol$ is an \emph{independent synchronisation} if and only if
  $x$ has no successor $a_j \in \Bv \cap \Proc$ such that $\exists a_i \in x$, $a_i \neq a_j$.
\end{definition}

\todo{intuition on sufficient condition}
Then, \pref{th:approxinf} gives a sufficient condition for the reachability of 
a local state in a given context
of an objective sequence in a given context
which is derived immediately from the saturated graph of local causality,
and the condition that all sets of hitters are coherent.
A proof of this theorem is given in \pref{suppl:demoapproxinf}.

\begin{theorem}[Under-approximation]
\label{th:approxinf}
  Given an AAN $(\PHs; \PHl; \PHa)$,
  a context $\ctx$ and an objective sequence $\w$,
  if the LCG $\cwB$ contains no cycle,
  all objective nodes have at least one child,
  and all the synchronisations are independent,
  then $\uconcr(\w) \neq \emptyset$.
\end{theorem}

@@

\modMF{
We note furthermore that in the case where
the method developed in this section is not conclusive,
it is possible to compute only a subset of $\Bv \cap \Sol$,
by removing some solutions from the initial graph of local causality $\myB$,
or by removing them from the saturated graph of local causality $\cwB$ and by trimming it.
In other words, this consists in ignoring some of the bounce sequences
for some of the objectives,
which intuitively cannot create false positives.
Indeed, \pref{th:approxinf} is then still valid on the partial graph obtained,
and this removal can lead to more conclusiveness by trimming parts of the graph
that were not necessary for the reachability
(especially cycles or unnecessary but inconclusive branches).
If one wants to try each possible subset of solutions,
then the overall method turns out to be exponential
in the number of solutions to each objective.
}

@@

In this section, we briefly explain an alternative sufficient condition that
progressively takes into account the successive objectives, instead of
considering all of them at a time, as it is done in \pref{ssec:ua}.
Because objectives are taken into account individually, such an approach
considers only a subset of scenarios.
However, because each iteration focuses on a smaller part of the network, this
sequential under-approximation may be more conclusive.

Let us define a sequence of objectives $\w=\obj{a_i}{a_j}\concat\w'$ with
$a_i\neq a_j$ and a state $s\in \PHl$ with $\get{s}{a}=a_i$.
One can remark that any scenario reaching $a_j$ necessarily includes one of the
bounce sequences in $\BS(\obj{a_i}{a_j})$, and, in particular,
any minimal scenario reaching $a_j$ ends in a state where $a_j$ is present but
also the hitters of the last bounce of one bounce sequence in $\BS(\obj{a_i}{a_j})$.
\pref{def:lastprocs} defines $\lastprocs(\obj{a_i}{a_j})$ as the set of set of
local states that may be present just after reaching $a_j$.

\begin{definition}[$\lastprocs : \Obj\to\Sol$]
\label{def:lastprocs}
  Given an objective $\obj{a_i}{a_j} \in \Obj$, $\lastprocs(\obj{a_i}{a_j})$ is
  defined as the largest set such that, $\forall ps\in\lastprocs(\obj{a_i}{a_j})$, 
  $ps\in\sSol$,
  \begin{enumerate}
    \item $a_j \in ps$;
    \item $\exists \zeta \in \BS(\obj{a_i}{a_j}),
      \hitter{\zeta_{\card{\zeta}}} \subseteq ps$;
    \item $\nexists ps' \in \lastprocs(\obj{a_i}{a_j}),
      ps' \subset ps \wedge ps' \neq ps$.
  \end{enumerate}
\end{definition}

\todo{integrate}
We also extend the override operator to contexts (\pref{def:ctxcap}).
\begin{definition}[$\Cap: \Ctx \times \powerset(\PHproc) \rightarrow \Ctx$]
\label{def:ctxcap}
  For any $\ctx\in\Ctx$ and set of local states $ps \in \powerset(\PHproc)$,
  the override of $\ctx$ by $ps$ is noted $\ctx \Cap ps$ and is defined by:
  \[ \forall a \in \PHs, \PHget{(\ctx \Cap ps)}{a} \DEF
  \begin{cases}
    \{ p \in ps \mid \PHsort(p)=a \} & \text{if } \exists p \in ps, \PHsort(p)=a,\\
    \PHget{\ctx}{a} & \text{else.}
  \end{cases}
  \]
\end{definition}

From \pref{th:approxinf}, we can deduce that
for any scenario $\delta$ in $\uconcr(P)$,
there exists a set of local states $ps\in\lastprocs(P)$
such that $ps \subseteq (s\play\delta)$.
Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
with $\ctx'=\ctx\Cap\procs(\mycwB{\ctx}{P})$,
there exists a scenario $\delta'$ concretising $\w'$ from the
state $(s\play\delta)$.
Therefore, the scenario $\delta\concat\delta'$ concretises
$\w$.

\begin{theorem}[Sequential under-approximation]
\label{thm:ordered-ua}
Given an AAN $(\PHs; \PHl; \PHa)$,
a context $\ctx$ and an objective sequence $\w =
P\concat\w'\in\OS$,
$\uconcr(P)\neq\emptyset \wedge
	\forall ps \in\lastprocs(P),
	\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset
	\Longrightarrow \uconcr(\w)\neq\emptyset$,
where $\ctx' = \ctx\Cap\procs(\mycwB{\ctx}{P})$.
\end{theorem}
\begin{proof}
If $\uconcr(P)\neq\emptyset$,
for all $s\in \PHl, s\subseteq\ctx$,
there exists a scenario $\delta\in\uconcr(P)\cap\Sce(s)$;
from \pref{def:lastprocs} and proof of \pref{th:approxinf},
$\exists ps\in\lastprocs(P)$ such that
$(s\play\delta)\subseteq\ctx'\Cap ps$.
Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
there exists a scenario $\delta'\in\muconcr_{\ctx'\Cap ps}(\w')$ such that
$\delta'\in\Sce(s\play\delta)$.
Hence, $\delta\concat\delta'$ is a scenario playable in $s$.
Therefore, for all $s\in \PHl, s\subseteq\ctx$, there exists a scenario
concretising $\w$.
Hence, $\uconcr(\w)\neq\emptyset$.
\end{proof}

>>>>

The existence of a scenario from a state $s$ leading to a state
where a given local state of an automaton $a_j$ is present
can be reformulated as the checking for the non-emptiness of $\concr(\obj{a_i}{a_j})$, where
$a_i=\get{s}{a}$.
A first hint for checking this emptiness is to look for actions that have to be played in order to
reach the state $j$ from $i$ within the automaton $a$.

@@

\begin{comment}
\todo{revise}
In the following, we denote: $\sSol = \powerset(\PHproc)$
\moda{%
and $\Sol = \powerset(\sSol)$.
}%
\modMF{%
The elements of $\sSol$ are sets of local states,
and will later represent sets of hitters of a given action
that are required to be active simultaneously in order to play this related action.
The elements in $\Sol$ are sets of sets of hitters,
and represent the requirements to play a whole bounce sequence.
}%

@@

  \noindent
  \modMF{
  As a consequence,
  $\aBS(\obj{a_i}{a_j}) = \emptyset$ if $\BS(\obj{a_i}{a_j}) = \emptyset$,
  and $\BS(\obj{a_i}{a_i}) = \{ \emptyset \}$.
  }%
\end{definition}
\end{comment}

@@

These refinements can be summarized compactly with a so-called Local Causality Graph (LCG).
Given an initial context $\ctx$ and a local state $p\in\Proc$,
A LCG $\cwB = (\cwV, \cwE)$
is a digraph where $\cwV \subseteq \Proc\cup \Obj \cup \Sol \cup \sSol$ is the set of vertices
where $\sSol=\powerset(\Proc)$ and $\Sol=\Obj\times\powerset(\sSol)$
and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges
(\pref{def:lcg}).
A node in $\Obj$ represents an objective that have to be refined.
Such a node can then be related to nodes in $\Sol$ which represents a set of hitter set of a
bounce sequence of the objective:
given an objective $P$, if $\zeta\in\BS(P)$, $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid
n\in\indexes\zeta \}$, then $P$ is related to $\langle P, \abstr\zeta\rangle\in\Sol$
(\pref{def:lcg}-3).
Given a node $\langle P,\abstr\zeta\rangle\in\cwV\cap\Sol$, for each $ps\in\abstr\zeta$,
it is related to a node $ps\in\sSol$
(\pref{def:lcg}-4).
A node $ps\in\sSol$ is then related to each $a\in\Proc$
(\pref{def:lcg}-5).
Given a node $a_i\in\cwV\cap\Proc$, for each $a_j\in\ctx$ or $a_j\in\cwV\cap\Proc$,
it is related to an objective $\obj{a_j}{a_i}$
(\pref{def:lcg}-2).
Finally, given a node $\obj{a_j}{a_i}\in\cwV\cap\Obj$,
if a local state $a_k\neq a_i$ is in its descendants (given by
$\conn_{(\cwBNodes,\cwBEdges)}(\obj{a_j}{a_i})$), then
$\obj{a_j}{a_i}$ is related to $\obj{a_k}{a_i}$ in the LCG
(\pref{def:lcg}-6).

\begin{definition}
\label{def:lcg}
Given a context $\ctx$ and a local state $p\in \Proc$,
the Local Causality Graph (LCG) for reachability under-approximation
$\cwB \DEF (\Bv, \Be)$
with
$\cwBNodes \subseteq \Proc \cup \Obj \cup \NSol \cup \sSol$
and
$\cwBEdges \subseteq \cwBNodes \times \cwBNodes$,
is the smallest graph such that:
\begin{enumerate}
\item
$p \in \cwBNodes$
\item
$a_i\in\cwBNodes\cap\Proc \Leftrightarrow \{ (a_i,\obj{a_j}{a_i}) \mid
a_j\in\ctx \vee a_j\in\cwBNodes\cap\Proc)
\}\subseteq\cwBEdges$
\item
$P\in\cwBNodes\cap\Obj \Leftrightarrow 
	\{ (P,\langle P,\abstr \zeta\rangle) \mid \zeta\in\BS(P) \}\subseteq\cwBEdges$
\item
$\langle P, nls \rangle\in\cwBNodes\cap\NSol \Leftrightarrow
	\{ (\langle P,nls\rangle, ls) \mid ls\in nls \}\subseteq\cwBEdges$
\item
$ls \in\cwBNodes\cap\sSol \Leftrightarrow
	\{ (ls, a_i) \mid a_i\in ls \}\subseteq\cwBEdges$
\item
$\obj{a_i}{a_j}\in \cwBNodes\cap\Obj \Rightarrow 
	\{(\obj{a_i}{a_j},\obj{a_k}{a_j}) \mid a_k\neq a_j,$
\\
\hspace*{4cm}
$a_k\in \conn_{(\cwBNodes,\cwBEdges)}(\langle\obj{a_i}{a_j},\abstr\zeta\rangle),$
\\
\hspace*{4cm}
$\zeta\in\BS(\obj{a_i}{a_j}) \}\subset\cwBEdges$
\end{enumerate}
with $\abstr\zeta \DEF \{\PHhitter(\zeta_n) \mid n\in\indexes\zeta \}$.
\end{definition}

@@

Given a context $\ctx$ and a local state $p\in\Proc$, the LCG $\cwB$ contains a set of objectives
that can be used to build a concrete scenario reaching $p$.
Because we are focused on sufficient conditions for reachability, we do not require that all
possible scenarios can be derived from the LCG.

In this section, we prove that if the LCG has no cycle, if all its nodes in $\Obj$ have at least one
child, and if all its nodes in $\sSol$ satisfy a
particular criteria, so-called independence, then from any state
delimited by the context $\ctx$, there exists a scenario that reaches $p$
(\pref{th:approxinf}).

A node $x$ of the LCG in $\sSol$ is \emph{independent} (\pref{def:coherent}) if for each local state
$a_i\in x$, none of the other local state $b_j\in x$ have a local state of automaton $a$ different
than $a_i$ in their descendants.
This criteria ensures that once a local state in $x$ has been reached, reaching another local state
in $x$ should not require to change the first local state.

\begin{definition}[Independent synchronisations]
\label{def:coherent}
  In a LCG $\cwB = (\Bv, \Be)$,
  a node $x \in \Bv\cap\sSol$ is \emph{independent} if and only if
  for each $a_i\in x$,
  for each $b_j\in x, b_j\neq a_i$,
  $a_k \in\conn_{\cwB}(x) \cap \Proc \Rightarrow a_k = a_i$.
\end{definition}

The intuition is the following.
Given a state $s\subset\ctx$, we recursively refine the initial objective (reaching $p$ from the initial
state) according to its children.
As the LCG is acyclic, such a recursion always terminates, and as all the objective nodes have at
least one child, it never get stuck.
The refinement of an objective node $\obj{a_i}{a_j}$ acts as follows:
if the node has another objective node $\obj{a_k}{a_j}$ as child, we first refine the objective
$\obj{a_i}{a_k}$ (which, by construction, is necessarily in the LCG)
and then will refine the objective $\obj{a_k}{a_j}$.
If the objective nodes has only nodes in $\Sol$ (bounce sequences), one is picked arbitrarily.
If $\langle P, nls\rangle$ is the chosen node,
by construction there exists $\zeta\in\BS(P)$ such that $\abstr\zeta = nls \in \powerset(\sSol)$.
If $\zeta = \emptyseq$ (for instance in the case when $a_i = a_j$), the recursion stops and we
continue to the next stage.
Otherwise, for each $n\in\indexes\zeta$,
for each $b_i \in\PHhitter(\zeta_n)$,
we refine the objective $\obj{b_j}{b_i}$ where $b_j$ is the state of $b$ in the current state.
By induction, $\obj{b_j}{b_i}$ is a child of $b_i$ in the LCG of \pref{def:lcg}.
Then, we know (by induction) that the current state of $b$ is $b_i$.
After having repeated this procedure for each $b_i\in\PHhitter(\zeta_n)$,
because all the nodes in $\sSol$, and in particular $\PHhitter(\zeta_n)$, are independent,
we know that all the local states in $\PHhitter(\zeta_n)$ are in the current state.
In addition, we know that the state of automaton $a$ has remained unchanged, otherwise
$\obj{a_i}{a_j}$ would have an objective child.
Hence, the action $\zeta_n$ is playable in the current state.
We apply this action, modifying the state of $a$ to $a_j$ and continue to the next stage.
At the end, this recursive procedures builds a scenario from $s\subset\ctx$ to a state containing $p$.

\begin{theorem}[Under-approximation]
\label{th:approxinf}
  Given an AAN $(\PHs; \PHl; \PHa)$,
  a context $\ctx$ and an objective sequence $\w$,
  if the LCG $\cwB$ contains no cycle,
  all nodes in $\Obj$ have at least one child,
  and all nodes in $\sSol$ are independent,
  then for any state $s\in\PHl$ such that $s\subset\ctx$,
  there exists a scenario $\delta\in\Sce$ with $p\in s\play\delta$.
\end{theorem}

@@

We note furthermore that the method does not require any completeness of the bounce sequences
$\BS$.
Therefore, in order to reduce the number of bounce sequences to consider, and potentially removing
cycles and non-satisfying nodes,
one can consider only a sub-set of, or single, bounce sequences for each objectives.
However, such an approach would imply to enumerate all possible combinations of bounce sequences
subsets, hence being exponential in the number of objectives having at least two bounce sequences.

@@

In this section, we briefly explain an alternative sufficient condition that
can be applied when looking for scenarios that successively reach a sequence of local states (e.g.,
first reach $a_j$, then later $b_k$, \ldots).

The approach proposed in this sub-section essentially applies the previous under-approximation for
the first local states, and then computes a set of contexts that may be considered as the starting
point for the next local states.
In that way, the local states to reach are taken into account separately, which implies that only a
subset of scenarios can be captured.
%However, because each iteration focuses on a smaller part of the network, this
%sequential under-approximation may be more conclusive.

\todo{computes possible outcomes from the LCG, gives it as context for the next stage}.
